\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-11 Articles/IROS/root.tex
added interpolation example

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\linewidth]{demo-field1.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:example-field}
\end{figure}

@@

@@

\subsection{Drone Example}

\add{EXAMPLE: DRONE MOVING THROUGH THE MAP OF OBSTACLES USING APF}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.95\linewidth]{demo-field1.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:example-field}
\end{figure}

\add{add label, caption, every plot has different axis scale}

@@

\subsection{Repulsive Field Interpolation}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{non_and_interp_4_plots.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:interp-experiment}
\end{figure}

@@

\remove{Drone Example}

\remove{EXAMPLE: DRONE MOVING THROUGH THE MAP OF OBSTACLES USING APF}
